Supporting Information

### 2018-03-14 SupportingInformation.Rmd
added a chunk in support of a Taylor's law analysis

>>>>

<!--make surrogate datasets for TL analysis to follow-->
```{r taylors_law_make_surrogs, echo=F, cache=T, cache.extra=list(seed,mtime("copsurrognd.R"))}
source("copsurrognd.R")
set.seed(seed)

#***constants
N<-100 #length of time series
n<-25 #number of sampling locations
numdat<-25 #the number of datasets to get from the normal copula
rho<-0.7 #normal-copula parameter for dependence between locations
          #this is a covariance, see below call to rmvnorm

#***generate the starting data, which has normal copula structure
#because it comes from a multivariate normal
sig<-matrix(rho,n,n)
diag(sig)<-1
m<-rmvnorm(N*numdat,mean=rep(0,n),sigma=sig)
m<-array(m,c(N,numdat,n))
m<-aperm(m,c(1,3,2))
gshape<-7.5
gscale<-1 #gamma parameters
cop_to_marg_trans<-function(x)
{
  return(qgamma(x,shape=gshape,scale=gscale)) #this is where we choose the marginals,
                                  #should be something skewed
}
marg_to_cop_trans<-function(x) #transforms to copula space
{
  return(pgamma(x,shape=gshape,scale=gscale))
}
m<-cop_to_marg_trans(pnorm(m))

#***surrogates using a Clayton copula, kendall preserving
#get the Clayton parameter to use
ncop<-normalCopula(rho,2)
ccop<-claytonCopula(2,2)
cparam<-iTau(ccop,tau(ncop))
ccop<-claytonCopula(cparam,n)

#generate the surrogates
csurrog<-array(NA,dim(m))
for (counter in 1:dim(m)[3])
{
  csurrog[,,counter]<-copsurrognd(m[,,counter],targetcop=ccop,numsurrog=1)
}

# #test to see whether kendalls are similar between m and csurrog - 
#only works at all as a test if N is large (I used 1000)
# cor(m[,1,1],m[,2,1],method='kendall')
# cor(csurrog[,1,1],csurrog[,2,1],method='kendall')
# cor(m[,3,1],m[,4,1],method='kendall')
# cor(csurrog[,3,1],csurrog[,4,1],method='kendall')
# cor(m[,5,1],m[,6,1],method='kendall')
# cor(csurrog[,5,1],csurrog[,6,1],method='kendall')
# 
# cor(m[,1,2],m[,2,2],method='kendall')
# cor(csurrog[,1,2],csurrog[,2,2],method='kendall')
# cor(m[,3,2],m[,4,2],method='kendall')
# cor(csurrog[,3,2],csurrog[,4,2],method='kendall')
# cor(m[,5,2],m[,6,2],method='kendall')
# cor(csurrog[,5,2],csurrog[,6,2],method='kendall')

#***surrogates using a Frank copula, kendall preserving
#get the Frank parameter to use
fcop<-frankCopula(4,2)
fparam<-iTau(fcop,tau(ncop))
fcop<-frankCopula(fparam,n)

#generate the surrogates
fsurrog<-array(NA,dim(m))
for (counter in 1:dim(m)[3])
{
  fsurrog[,,counter]<-copsurrognd(m[,,counter],targetcop=fcop,numsurrog=1)
}

#***surrogates using a survival Clayton, kendall preserving
#take the clayton surrogates and transform them to the 
#copula space, then flip, then transform back
scsurrog<-cop_to_marg_trans((1-marg_to_cop_trans(csurrog)))

# #test: should have identical taus as csurrog
# cor(csurrog[,1,1],csurrog[,2,1],meth='kendall')
# cor(scsurrog[,1,1],scsurrog[,2,1],meth='kendall')
# cor(csurrog[,1,2],csurrog[,2,2],meth='kendall')
# cor(scsurrog[,1,2],scsurrog[,2,2],meth='kendall')

kend.surrog<-list(cla=csurrog,nor=m,fra=fsurrog,scl=scsurrog)

#***surrogates using a Clayton copula, spearman preserving
#get the Clayton parameter to use
ccop<-claytonCopula(2,2)
cparam<-iRho(ccop,rho(ncop))
ccop<-claytonCopula(cparam,n)

#generate the surrogates
csurrog<-array(NA,dim(m))
for (counter in 1:dim(m)[3])
{
  csurrog[,,counter]<-copsurrognd(m[,,counter],targetcop=ccop,numsurrog=1)
}

#***surrogates using a Frank copula, spearman preserving
#get the Frank parameter to use
fcop<-frankCopula(4,2)
fparam<-iRho(fcop,rho(ncop))
fcop<-frankCopula(fparam,n)

#generate the surrogates
fsurrog<-array(NA,dim(m))
for (counter in 1:dim(m)[3])
{
  fsurrog[,,counter]<-copsurrognd(m[,,counter],targetcop=fcop,numsurrog=1)
}

#***surrogates using a survival Clayton, spearman preserving
#take the clayton surrogates and transform them to the 
#copula space, then flip, then transform back
scsurrog<-cop_to_marg_trans((1-marg_to_cop_trans(csurrog)))

spea.surrog<-list(cla=csurrog,nor=m,fra=fsurrog,scl=scsurrog)
```
